A quantitative analysis of Media Agenda and Public Opinion using time-evolving topic distribution

### 2018-09-11 bmc_article.tex
Cambios finales

\par The mass media plays a fundamental role in opinion formation and therefore, it’s of vital importance to have an accurate quantitative description of the Media and Public Agenda and their relationship in the framework of agenda-setting theory. In this work, through the implementation of a topic detection algorithm we describe the Media Agenda as a distribution which evolves with time and which is defined in a topic space which emerges intrinsically from the corpus. This gave us an insight of how we can construct and follow the audience interests, i.e the Public Agenda, in order to compare with the media interests.

\par This approach with newspaper, Twitter and Google trends data, lets us understand that the Public Agenda is usually less diverse than the Media Agenda. Specifically, it is shown that when there is a very attractive topic, the audience naturally focuses only on this one. On the other hand, the media keeps a certain degree of diversity and a wider range of topics.

\par Interestingly, we show how the measurement of distances between agendas can be employed to rapidly detect those periods when the public may have an independent behaviour respect to the media and also when it does not. The ``Missing person" topic analysis, presented in figure  \ref{fig:Maldonado_setagenda}, shows concrete evidence of a complex dynamics agenda-setting case. Therefore, this work depicts a methodology which can be used in order to understand who sets the agenda: If it is a media outlet or the society.  [SEBAS .... agregar alguna linea de texto de porque esto es muy bueno]

>>>>

\par The mass media plays a fundamental role in opinion formation and therefore, it is of vital importance to have an accurate quantitative description of the Media and Public Agenda and their relationship in the framework of agenda-setting theory. In this work, through the implementation of a topic detection algorithm we describe the Media Agenda as a distribution which evolves with time and which is defined in a topic space which emerges intrinsically from the corpus. This gave us an insight of how we can construct and follow the audience interests, i.e the Public Agenda, in order to compare with the media interests.

\par This approach with newspaper, Twitter and Google trends data, let us understand that the Public Agenda is usually less diverse than the Media Agenda. Specifically, it is shown that when there is a very attractive topic, the audience naturally focuses only on this one. On the other hand, the media keeps a certain degree of diversity and a wider range of topics.

\par Interestingly, we show how the measurement of distances between agendas can be employed to rapidly detect those periods when the public may have an independent behaviour respect to the media and also when it does not. The ``Missing person" topic analysis, presented in figure  \ref{fig:Maldonado_setagenda}, shows concrete evidence of a complex dynamics agenda-setting case. 
Therefore, this work depicts a very general methodology which can be used in order to understand who sets the agenda: If it is the media or the society. 
The generality of our method allows to easily face up the agenda-setting issue in other datasets.
